### 2015-01-17 src/discussion.Rnw
add some discussion

To be added.

>>>>

We will analyze each of the different types of mutation reduction strategies in
detail, and summarize the broad patterns we see at the end.

\subsubsection{Operator Selection}
From Table~\ref{tbl:selective}, we see that except for statement deletion, we
have negative utility in comparison to baseline for both tests and asserts.
Even for statement deleition, the utility is just 0.5 tests better than
baseline. A similar result is present in the strategy effectiveness also,
where the effectiveness over baseline is either negettive or extremely small.

This is corroborated by statistical analysis where using paired t-test given in
Table~\ref{tbl:ttests}, it was found that the test utiilty was lower than
baseline for selective mutation strategies except statement deletion
($p < 0.01$), and strategy effectiveness was found to be lower than baseline,
but not significant.

For statement deletion, while utility was found to be positive ($p < 0.05$),
the magnitude was less than a single test.

For N-selection, which is given in Table~\ref{tbl:nselection}, the situation
is similar a few steps in operator removal seem to indicate a positive utility
and a positive strategy effectiveness. However, as Table~\ref{tbl:ttests}
shows, the mean utility is mostly negative, and for strategy effectiveness,
the magnitude is very low~\footnote{The difference between
Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests} is due to test or mutant
number being zero for baseline, and hence remvoed for computing percentage}.

The strategy of selecting a single operator in Table~\ref{tbl:singles} also
does not seem to do very well, with either negative or very small positive
utility and strategy effectiveness when compared to baseline.

\subsubsection{Sampling over program elements}
For sampling over program elements in Table~\ref{tbl:element}, and t-tests
in Table~\ref{tbl:ttests}, there appears to be a consistent advantage. However,
even this advantage is extremely small with roughly 1 test utility or less
than $6$ mutants advantage for strategy effectiveness.

\subsubsection{Operator based x\% sampling}
The operator based sampling given in Table~\ref{tbl:opsample} and t-tests in
Table~\ref{tbl:ttests}, we see that there is a small positive test utility.
However, as before, the magnitude is very low to be of practical significance.

A general pattern that we can glean from this analysis is that none of the
mutation reduction strategies appear to be practically better than the simplest
strategy of all, the random selection strategy. This suggests that at least
from the perspective of a software tester wishing to use mutation analysis
as an evaluation criteria to judge when or which tests to add, random sampling
is the easiest way to reduce the computational requirements of mutation
analysis. This assumes even more importance when we consider that the adequate
random sample of mutants increases at a rate less than $O(n^\frac{1}{4})$ when
the program size increases linearly~\cite{zhang2014empirical}.

### 2015-01-17 src/tbl.ttests.Rnw
add some discussion

>>>>

t.test.table['Op-Selection nmc',]            <- c(nmc.t$estimate,nmc.t$conf.int[1],nmc.t$conf.int[2],nmc.t$p.value, nmc.m$estimate,nmc.m$conf.int[1],nmc.m$conf.int[2],nmc.m$p.value)
t.test.table['Op-Selection rv',]            <- c(rv.t$estimate,rv.t$conf.int[1],rv.t$conf.int[2],rv.t$p.value, rv.m$estimate,rv.m$conf.int[1],rv.m$conf.int[2],rv.m$p.value)
t.test.table['Op-Selection ic',]            <- c(ic.t$estimate,ic.t$conf.int[1],ic.t$conf.int[2],ic.t$p.value, ic.m$estimate,ic.m$conf.int[1],ic.m$conf.int[2],ic.m$p.value)
t.test.table['Op-Selection dc',]            <- c(dc.t$estimate,dc.t$conf.int[1],dc.t$conf.int[2],dc.t$p.value, dc.m$estimate,dc.m$conf.int[1],dc.m$conf.int[2],dc.m$p.value)
t.test.table['Op-Selection nc',]            <- c(nc.t$estimate,nc.t$conf.int[1],nc.t$conf.int[2],nc.t$p.value, nc.m$estimate,nc.m$conf.int[1],nc.m$conf.int[2],nc.m$p.value)
t.test.table['Op-Selection rc',]            <- c(rc.t$estimate,rc.t$conf.int[1],rc.t$conf.int[2],rc.t$p.value, rc.m$estimate,rc.m$conf.int[1],rc.m$conf.int[2],rc.m$p.value)
t.test.table['Op-Selection vmc',]            <- c(vmc.t$estimate,vmc.t$conf.int[1],vmc.t$conf.int[2],vmc.t$p.value, vmc.m$estimate,vmc.m$conf.int[1],vmc.m$conf.int[2],vmc.m$p.value)
t.test.table['Op-Selection m',]            <- c(m.t$estimate,m.t$conf.int[1],m.t$conf.int[2],m.t$p.value, m.m$estimate,m.m$conf.int[1],m.m$conf.int[2],m.m$p.value)
t.test.table['Op-Selection cb',]            <- c(cb.t$estimate,cb.t$conf.int[1],cb.t$conf.int[2],cb.t$p.value, cb.m$estimate,cb.m$conf.int[1],cb.m$conf.int[2],cb.m$p.value)
t.test.table['Op-Selection i',]            <- c(i.t$estimate,i.t$conf.int[1],i.t$conf.int[2],i.t$p.value, i.m$estimate,i.m$conf.int[1],i.m$conf.int[2],i.m$p.value)
t.test.table['Op-Selection ri',]            <- c(ri.t$estimate,ri.t$conf.int[1],ri.t$conf.int[2],ri.t$p.value, ri.m$estimate,ri.m$conf.int[1],ri.m$conf.int[2],ri.m$p.value)
t.test.table['Op-Selection rs',]            <- c(rs.t$estimate,rs.t$conf.int[1],rs.t$conf.int[2],rs.t$p.value, rs.m$estimate,rs.m$conf.int[1],rs.m$conf.int[2],rs.m$p.value)
t.test.table['Op-Selection es',]            <- c(es.t$estimate,es.t$conf.int[1],es.t$conf.int[2],es.t$p.value, es.m$estimate,es.m$conf.int[1],es.m$conf.int[2],es.m$p.value)
t.test.table['Op-Selection in',]            <- c(in.t$estimate,in.t$conf.int[1],in.t$conf.int[2],in.t$p.value, in.m$estimate,in.m$conf.int[1],in.m$conf.int[2],in.m$p.value)

### 2015-01-17 src/ttests.Rnw
add some discussion

>>>>

db <- subset(common.db, operator=="nmc")
nmc.t <- mintc.t.test(db)
nmc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rv")
rv.t <- mintc.t.test(db)
rv.m <- mutant.t.test(db)

db <- subset(common.db, operator=="ic")
ic.t <- mintc.t.test(db)
ic.m <- mutant.t.test(db)

db <- subset(common.db, operator=="dc")
dc.t <- mintc.t.test(db)
dc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="nc")
nc.t <- mintc.t.test(db)
nc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rc")
rc.t <- mintc.t.test(db)
rc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="vmc")
vmc.t <- mintc.t.test(db)
vmc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="cc")
cc.t <- mintc.t.test(db)
cc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="emv")
emv.t <- mintc.t.test(db)
emv.m <- mutant.t.test(db)

db <- subset(common.db, operator=="m")
m.t <- mintc.t.test(db)
m.m <- mutant.t.test(db)

db <- subset(common.db, operator=="cb")
cb.t <- mintc.t.test(db)
cb.m <- mutant.t.test(db)

db <- subset(common.db, operator=="i")
i.t <- mintc.t.test(db)
i.m <- mutant.t.test(db)

db <- subset(common.db, operator=="ri")
ri.t <- mintc.t.test(db)
ri.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rs")
rs.t <- mintc.t.test(db)
rs.m <- mutant.t.test(db)

db <- subset(common.db, operator=="es")
es.t <- mintc.t.test(db)
es.m <- mutant.t.test(db)

db <- subset(common.db, operator=="in")
in.t <- mintc.t.test(db)
in.m <- mutant.t.test(db)
